---
title: "Untitled"
author: "Srisha Gorasa"
date: "5/9/2021"
output: word_document
---
```{r}
#Installing package if it is not present
package_listing <- c('data.table', 'tidyverse','DT' , 'leaflet','plotly','ggthemes')

for (required_package in package_listing) {
  if (!require(required_package, character.only = T, quietly = T)) {
    install.packages(required_package, repos = "http://cran.us.r-project.org")
    library(required_package, character.only = T)
  }
}
```

```{r}
#Loading the packages
library(data.table)
library(tidyverse)
library(DT)
library(plotly)
library(corrplot)
library(caret)
library(class)
library(ggthemes)     # ggplot themes
library(randomForest)
library(pROC)
library("verification")
library(kernlab)      # SVM methodology
library(e1071)        # SVM methodology
library(RColorBrewer) # customized coloring of plots for svm
```

```{r}
breast.data <- read.csv("/Users/srishachandragiri/Downloads/data.csv")
```

```{r}
str(breast.data)
```
```{r}
fwrite(x = as.data.frame(summary(breast.data)), file = "foo.csv")

breast.data[,33] <- NULL # Lat column had NA values. Removing it

sum(is.null(breast.data)) #No NA values
```

```{r}
breast.data[duplicated(breast.data)]  # 0 duplicates
```

```{r}
prop.table(table(breast.data$diagnosis)) # Class imbalance with 62% benign and 37% malignant
```
The dataset contained one columns in which all the values were missing. This column was removed from the dataset. Apart from this the data didn’t contain any missing values.
The dataset contained 0 duplicate values
62% are benign and 37% are malignant cancer cases in the dataset.
The dataset does contain a column where all values are null values. This column was dropped from the dataset.
